|

### 2024-08-11 doc/paper.qmd
again update paper.qmd

### Discretion in Reported Earnings: Small Loss Avoidance (EM4)
EM4 captures the extent to which firms manage their reported earnings to avoid small losses. This is an important measure that quantifies the propensity of firms to avoid small losses through earnings management. By calculating the ratio of small profits to small losses, it provides a clear indication of how widespread this practice is within a particular country. A higher EM4 value suggests that firms in a given country are more likely to use accounting discretion to convert small losses into small profits, reflecting a tendency toward earnings management. Note that I used `item1651` (Net Income before Preferred Dividends) as the variable for net earnings, as mentioned in @sec-step2_preparation.

@@

This final assignment required the comprehensive application of all the skills learned and feedback received from previous assignments, making it a more complex project workflow. In the future, this repository can be cloned or forked (if made public) to kickstart further projects on earnings management measures analysis. Thanks for reading!

>>>>

### Discretion in Reported Earnings: Small Loss Avoidance (EM4)
EM4 captures the extent to which firms manage their reported earnings to avoid small losses. This is an important measure that quantifies the propensity of firms to avoid small losses through earnings management. By calculating the ratio of small profits to small losses, it provides a clear indication of how widespread this practice is within a particular country. A higher EM4 value suggests that firms in a given country are more likely to use accounting discretion to convert small losses into small profits, reflecting a tendency toward earnings management. Note that I used `item1651` (Net Income before Preferred Dividends) as the variable for net earnings, as mentioned in @sec-step2_preparation. I also ensured that each country included in the EM4 calculation had at least five small loss observations, as per the methodology outlined by @Leuz_2003. The review found that no countries were excluded from the analysis due to this criterion.

@@

This final assignment required the comprehensive application of all the skills learned and feedback received from previous assignments, making it a more complex project workflow. In the future, this repository can be cloned or forked (if made public) to kickstart further projects on earnings management measures analysis. Additionally, the included presentation template can be rendered alongside the paper for further academic use, providing a visually engaging summary of the research findings. Thanks for reading!
